\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd
Updates on 31 Auguts

  - name          : "Rafael Robert Lazar"
    affiliation   : "2"
    role:
      - Writing - Original Draft Preparation

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Methods

@@

>>>>

  - name          : "Rafael Robert Lazar"
    affiliation   : "2"
    role:
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization
  - name          : "Manuel Spitschan "
    affiliation   : "3"
    corresponding : yes   
    address       : ""
    email         : ""
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia"
  - id            : "2"
    institution   : "University of Basel"

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction

# Methods

@@

This line is just a test for pushing in the github repo.
